Compositional Equivalences Based on Open pNets

### 2022-10-17 2016-Weak-FH-Bisim/WeakBisim.tex
mucrl2 V0

Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:2002, BaldanBB:07,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:2002,BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is that the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire. Logical formulae are suitable formalisms that capture the general class of components that can act as the placeholders of the system during its evolution. In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions. Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
Quotienting and decomposition techniques \cite{Larsen:91,LaveauxWillemse:ICE21} seem closer to our approach as they propose to 
overcome the state-space-explosion problem by decomposing formulas to be verified according to the process composition. 
However these techniques are expressed in a very different setting from ours and it is difficult to precisely relate them to the more structural and parameterised point of view we adopt here.
We could try to apply such automatic decomposition techniques to open pNets, but deriving a decomposition  for systems synchronised in a very parameterised way like we do requires further investigations.
Both parallel composition~\cite{Larsen:91} and mCRL2~\cite{LaveauxWillemse:ICE21} feature a concrete verification setting where decomposition is useful, while open automata provide a more general setting that could be used to represent both frameworks and hopefully generalise process decomposition results of \cite{Larsen:91,LaveauxWillemse:ICE21}.

>>>>

Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:2002, BaldanBB:07,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches. Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:2002,BaldanBB:07}, where both approaches are based
on some kinds of labelled transition systems. The distinguishing feature of their approach is that the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire. Logical formulae are suitable formalisms that capture the general class of components that can act as the placeholders of the system during its evolution. In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions. Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
mCRL2~\cite{} is another effective model for specifying and proving properties of concurrent systems. mCRL2 has an established tool-suite and share similarities with pNets. However, pNets feature hierarchical composition with more structure than mCRL2 that composes processes with a parallel operator. Synchronisation of processes is expressed very differently; it is difficult to precisely compare multi-actions of mCRL2 with synchronisation vectors of pNets but synchronisation vector ogf pNets enforce a  synchronisation based on the structure while in mCRL2 synchronisation is specified in a versatile, flexible, but less structured way.

Quotienting of process algebras~\cite{Larsen:91} and decomposition techniques for MCRL2~\cite{LaveauxWillemse:ICE21} share similarities with our approach; they propose to 
overcome the state-space-explosion problem by decomposing formulas to be verified according to the process composition. The decomposed problem must be equivalent to the original one.
However these techniques are expressed in a very different setting from ours and it is difficult to precisely relate them to the more structural and parameterised point of view we adopt here.
We could try to apply such automatic decomposition techniques to open pNets, but deriving a decomposition  for systems synchronised in a very parameterised way like we do requires further investigations.
Both parallel composition~\cite{Larsen:91} and mCRL2~\cite{LaveauxWillemse:ICE21} feature a concrete verification setting where decomposition is useful, while open automata provide a more general setting that could be used to represent both frameworks and hopefully generalise process decomposition results of \cite{Larsen:91,LaveauxWillemse:ICE21}.
